---
title: "What's going on in Airbnb Market?"
description: |
  Founded in 2008 by Brian Chesky, Nathan Blecharczyk, and Joe Gebbia, Airbnb,Inc. is more than an online platform that connects people who want to rent out their homes with people who are looking for accommodations in that locale. It represents a revolution on vacationing, shifting consumer behavior from booking traditional hotels to staying in someone else's home. Comparing with hotels which usually have homogenized rooms and commonplace experience, the platform offers cheaper prices, more authentic and unique experience for their customers. For example, Airbnb can be an apartment in New York, an eco bamboo home in Bali, a Castle in France, or even a snow igloo in Finland. It currently covers more than 191 countries and 81,000 cities around the world. On December 10, 2020, the company went public and was valued at over $100 billion. 
author:
  - name: Jiashu Liu
date: 12-17-2020
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(tidyverse)     # for data cleaning and plotting
library(googlesheets4) # for reading googlesheet data
library(lubridate)     # for date manipulation
library(openintro)     # for the abbr2state() function
library(maps)          # for map data
library(ggmap)         # for mapping points on maps
library(gplots)        # for col2hex() function
library(RColorBrewer)  # for color palettes
library(sf)            # for working with spatial data
library(leaflet)       # for highly customizable mapping
library(ggthemes)      # for more themes (including theme_map())
library(plotly)        # for the ggplotly() - basic interactivity
library(gganimate)     # for adding animation layers to ggplots
library(gifski)        # for creating the gif (don't need to load this library every time,but need it installed)
library(transformr)    # for "tweening" (gganimate)
library(shiny)         # for creating interactive apps
library(patchwork)     # for nicely combining ggplot2 graphs  
library(gt)            # for creating nice tables
library(rvest)         # for scraping data
library(robotstxt)     # for checking if you can scrape data
library(paletteer)
library(readr)
gs4_deauth()           # To not have to authorize each time you knit.
theme_set(theme_minimal())
```
```{r}
AB_US_2020 <- read_csv("~/Desktop/Advanced_Data_Science_in_R/JiashuLiu_distill/Airbnb/AB_US_2020.csv", 
    col_types = cols(id = col_character(), 
        host_id = col_skip(), neighbourhood = col_character()))
```

# *Introduction*

Founded in 2008 by Brian Chesky, Nathan Blecharczyk, and Joe Gebbia, Airbnb,Inc. is more than an online platform that connects people who want to rent out their homes with people who are looking for accommodations in that locale. It represents a revolution on vacationing, shifting consumer behavior from booking traditional hotels to staying in someone else's home. Comparing with hotels which usually have homogenized rooms and commonplace experience, the platform offers cheaper prices, more authentic and unique experience for their customers. For example, Airbnb can be an apartment in New York, an eco bamboo home in Bali, a Castle in France, or even a snow igloo in Finland. It currently covers more than 191 countries and 81,000 cities around the world. On December 10, 2020, the company went public and was valued at over $100 billion. 

In this research, I focus on evaluating how different aspects, such as locations and room types, affect the price of Airbnbs in the United States. The dataset is collected from [](https://www.kaggle.com/kritikseth/us-airbnb-open-data). The dataset includes ten regions across the U.S., and four room types including shared room, hotel room, private room, and entire home/apartment. To make our research more useful to common people, I lower the price level to under $2000 per night.

# *Will locations affect the price of Airbnbs?*

The answer is: YES! Let's first take a look at the number of Airbnbs in each region. From figure 1, we can see that the top three regions in our sample are Austin, Broward County, and Hawaii. Hawaii, as one of the most popular destinations for travelers, has 17,349 Airbnbs in total, and both Broward County and Austin have more than 10,000. As the second-most populous county in the state of Florida, there are lots of travel spots that make the county becomes popular. 

To look further into details, I created a density plot in figure 2 to present the price distribution of airbnbs in each region. It is interesting to see that all the regions have a right-skewed price distribution. On each region's density plot, I indicate the average price by a vertical black line. If we compare the average Airbnb price of each region, we can see that Hawaii has the highest average price of nearly 250 dollars per night. But to my surprise, among all ten regions in my sample, Chicago is the one that has the lowest average price of about 137 dollars per night.   
```{r}
figure1<-AB_US_2020%>%
  group_by(city)%>%
  summarise(host_id = n())%>%
  mutate(Number_of_Airbnb = host_id)%>%
  ungroup()%>%
  arrange(Number_of_Airbnb)%>%
  ggplot()+
  geom_col(aes(x = reorder(city, Number_of_Airbnb), 
               y = Number_of_Airbnb,
               fill = city))+
  labs(x = "", 
       y = "", 
       title = "Figure 1. The Number of Airbnbs in Each Region")+
  theme_minimal()+
  theme(legend.position = "none")

ggplotly(figure1)
```

```{r}
Average_price<-
  AB_US_2020%>%
  filter(price < 2000)%>%
  group_by(city)%>%
  summarise(host_id = n(),
            Average_price = mean(price))
  
aribnb_graph<-AB_US_2020%>%
  filter(price<2000)%>%
  mutate(city = fct_reorder(city, price, mean))%>%
  ggplot()+
  facet_wrap(vars(city), scales = "free_y", ncol = 2)+
  geom_density(mapping = aes(x=price, fill = city), alpha = 0.6)+
  geom_vline(data = Average_price, 
             mapping = aes(xintercept=Average_price),
             color = "black")+
  labs(x = "",
       y = "",
      title = "Figure 2. Price Distribution of Airbnbs in Each Region")+
  theme_minimal()+
  theme(legend.position = "none", axis.text.y = element_blank())

ggplotly(aribnb_graph)
```

# * *Will the room type affects the price of Airbnbs?* *

Before answering this question, let's first take a look at the number of Airbnbs in each room type. The platform offers different kinds of room types for their customers to choose from. In this dataset, we only include four room types: share room, hotel room, private room, and Entire home/apartment. You might be surprised to see there are hotel rooms listed in the dataset. But YES, you can use Airbnbs to book hotels. It's all based on your preference. As the platform becomes more and more popular, many hotels choose to join Airbnb's network. Figure 3. shows that most Airbnbs in the ten regions are 
entire home/apartments or private rooms. There are very few shared rooms or hotel rooms. I think the reason why an entire home/apartment becomes so popular is that this room type provides travelers, especially middle-class travelers who can afford higher prices, a better experience. Moreover, an entire home/apartment is also an excellent choice for family vacations. 

To further explore this problem, I created a group of density plots to show the price distribution of Airbnbs with different room types. Similar to what I did in Figure 2, I also indicate the average price of each room type using a vertical black line. Figure 4 reflects that the price distributions of all four room types are right-skewed. Among the four room types, the hotel room has the highest average price of about 234 dollars per night, while the shared room has the lowest average price of about 60 dollars per night. We can conclude that within the regions, travelers will have to pay more if they choose to book hotels. The reason why hotels still have higher prices even though they join Airbnb's network might be that hotels generally have higher costs. For example, their costs include but are not limited to professional fees, contingency, operating supplies & equipment, freight, and sales tax. In contrast, an individual host has a more simple cost structure. Therefore, at least in the regions we choose, room type is an important aspect influencing the price of Airbnbs. 
```{r}
room_type_data<-AB_US_2020%>%
  group_by(room_type)%>%
  summarise(host_id = n())%>%
  mutate(Number_of_Airbnb = host_id)%>%
  arrange(Number_of_Airbnb)

room_type_graph<-ggplot()+
  geom_col(room_type_data,
           mapping = aes(x = reorder(room_type, Number_of_Airbnb), 
                         y = Number_of_Airbnb,fill = room_type))+
  labs(x = "", 
       y = "", 
       title = "Figure 3. The Number of Airbnbs in Each Room Type")+
  theme_minimal()+
  theme(legend.position = "none")

ggplotly(room_type_graph)
```

```{r}
Room_type_average<-
  AB_US_2020%>%
  filter(price<2000)%>%
  group_by(room_type)%>%
  summarise(host_id = n(),
            Average_price = mean(price))

room_type_graph<-AB_US_2020%>%
  filter(price<2000)%>%
  mutate(room_type = fct_reorder(room_type, price, mean))%>%
  ggplot()+
  facet_wrap(vars(room_type), scales = "free_y", ncol = 1)+
  geom_density(mapping = aes(x=price, 
              fill = room_type), alpha = 0.6)+
  geom_vline(Room_type_average, 
             mapping = aes(xintercept = Average_price),
              color = "black")+
  labs(x = "",
       y = "",
       title = "Figure 4. Price Distribution of Airbnb in Each Room Type")+
  theme_minimal()+
  theme(legend.position = "none", axis.text.y = element_blank())

ggplotly(room_type_graph)
```

# *Availability and Price*

Finally, we can take a look at the availability of Airbnbs in each region and examine whether it affects the price or not. To reach that goal, I created a map using the leaflet() function. If we zoom in on the map below, we can see that the regions are colored by their availability throughout the year. The map reflects that many places in Hawaii are available more than 300 days in a year. As we discussed before, among the ten regions, Hawaii's Airbnbs have the highest average price, and it also has the largest number of Airbnbs. Therefore, the capability to accept tourists for more than 300 days in a year might also be another factor that drives up the average price. Austin also has high availability comparing to other regions. It has a high average price and a large number of Airbnbs. Therefore, we can conclude that availability is  a factor that influences the price of Airbnbs in different regions. 
```{r}
pal <- colorNumeric("viridis",
                   domain = AB_US_2020$availability_365,
                   reverse = TRUE)
leaflet(AB_US_2020)%>%
  addProviderTiles(providers$Stamen.TonerHybrid) %>% 
  addCircles(label = ~paste(city), 
             weight = 1, 
             opacity = 1,
             color = ~pal(availability_365))%>%
  addLegend(position = "bottomleft",
            pal = pal, 
            opacity = .7,
            values = ~availability_365, 
            title = "")
```

# *Summary*
In this research project, we examine how the three aspects--locations, room type, and availability--affect the price of Airbnbs in the U.S. When exploring the effect of locations, we randomly chose ten regions from the dataset, including Cambridge, Columbus, Asheville, Boston, Denver, Clark County, Austin, Broward County, and Hawaii, to narrow down the scope. The results show regions, where tourism plays an essential role in the local economy, will have more Airbnbs, and the price of the Airbnbs will be relatively higher. We also see that among the four room types, the entire home/apartment is the most attractive type, and the most expensive one as well. The availability is closely related to the locations. If more places in a region that can accept travelers more than 300 days in a year, the average price of Airbnbs in those regions will be higher. I think there are also other factors that might influence the price of Airbnbs but not included in this dataset, especially under this special time, and I will explore more on this topic in the future. 
