---
title: "Tidy_Tuesday1"
description: |
  A short description of the post.
author:
  - name: Jiashu Liu
date: 09-13-2021
output:
  distill::distill_article:
    self_contained: false
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
tuesdata <- tidytuesdayR::tt_load('2021-08-31')
tuesdata <- tidytuesdayR::tt_load(2021, week = 36)

bird_baths <- tuesdata$bird_baths
```

```{r}
library(tidyverse)    
library(lubridate)
library(ggthemes)    
```

```{r}
glimpse(bird_baths)
```
In this Tidy Tuesday homework, I explored the bird_bath data. The graph below is a grouped bar graph, presenting the number of birds in the rural and urban area of each bioregion in Austrilia respectively. The bird_count should be a binary factor indicating  whether a given species was present or absent at a bird bath. However, I calculated the number of occurance of birds at bath by cumulating the bird_count and grouping the data by bioregions and rural_urban area. it is well noticed that in Sydney Basin, bird baths present more in the urban area rather than rural area. There are also a lot NA in this dataset, which I think is attributed to the difficulty of collecting the data. 

```{r}
bird_baths%>%
  group_by(bioregions, urban_rural)%>%
  summarise(cumulative_bird_count=sum(bird_count))%>%
  ggplot(aes(y=bioregions, x=cumulative_bird_count, fill=urban_rural))+
  geom_bar(position="dodge", stat="identity")+
  labs(y="Bioregions", x="Occurance of birds at bath", title = "Number of birds in the rural and urban area of each bioregion")+
  theme_light()
```


